An application of Graph Theory to MDAO problem formulation

### 2012-10-12 intro.tex
stuff

    [TODO: insert XDSM for simple problem solved with MDF here]

    Although XDSM captures part functional aspects of FDT, it  leaves out the variables themselves. As a result, all variable information is aggregated 
    so that for the problem from Eqn. \ref{eqn:simple_fpf} you can say that $A$ depends on $B$ or vice versa, but you can't identify which 
    individual variables are interacting in the dependency cycle. Without the detailed variable information, you can't construct the compatibility 
    constraints necessary to implement the problem. Additionally, XDSM requires the use of solver and optimizer blocks to represent 
    the relationship between design variables and objectives/constraints. By introducing solver or optimizer blocks XDSM automatically provides
    some kind of solution strategy. Hence XDSM is too specific for use with a fundamental problem formulation.

    By taking XDSM, removing the requirement for solver/optimizer nodes and adding in nodes for each variable we are able to fully describe 
    the problem formulation for a general MDAO problem. In the following sections we describe the necessary syntax for specifying a 
    problem formulation withing a DSM and show how to make use of the resulting graph to find the FPF from any given graph. For completeness we 
    also present algorithms for converting between the general DSM and the more specific formulations discussed above.

>>>>

    \begin{figure}
        \begin{center}
        \includegraphics[height=.25\textheight]{XDSM/simple}
        \caption{XDSM for Eqn. \ref{eqn:simple}, with a gauss-siedel iteration and MDF solution architecture. \label{fig:XDSM_simple}}
        \end{center}
    \end{figure}

    Although XDSM captures part functional aspects of FDT, it  leaves out the variables themselves. As a result, all variable information is aggregated 
    so that for the problem from Eqn. \ref{eqn:simple_fpf} you can say that $A$ depends on $B$ or vice versa, but you can't identify which 
    individual variables are interacting in the dependency cycle. Without the detailed variable information, you can't construct the compatibility 
    constraints necessary to implement the problem. Additionally, XDSM requires the use of solver and optimizer blocks to represent 
    the relationship between design variables and objectives/constraints. By introducing solver or optimizer blocks XDSM automatically provides
    some kind of solution strategy. The XDSM for Eqn. \ref{eqn:simple} is given in Figure \ref{fig:XDSM_simple}. 
    This diagram is shown with an assumed gauss-siedel iteration scheme and a MDF solution architecture. 
    Hence XDSM is too specific for use with a fundamental problem formulation.

    By taking XDSM, removing the solver/optimizer nodes and adding in nodes for each variable we are able to fully describe 
    the problem formulation for a general MDAO problem. In the following sections we describe the necessary syntax for specifying a 
    problem formulation withing a DSM and show how to make use of the resulting graph to find the FPF from any given graph. For completeness we 
    also present algorithms for converting between the general DSM and the more specific formulations discussed above.
